### 2016-11-11 thesis/intro/intro.tex
finished physiological mechanism of obesity

In \gls{pomc}/\gls{cart} neuron, binding of leptin to its recpetor causes a depolarisation of the neuron \citep{Cowley2001}.
Together with the indirect effect from the \gls{npy}/\gls{agrp} neuron, leptin inhibits the \gls{pomc}/\gls{cart} neuron to release $\alpha$-\gls{msh}, and therefore sends a satiety signal to its downstream effector neurons.
\\

@@

It was first noticed by \citet{Spanswick1997} that insulin showed a very similar 
\\

\noindent
The last hormone is the \gls{pyy}, a peptide hormone released by the distal gastrointestinal tract that produces an anorexogenic signal.
\citep{Batterham2002}

>>>>

In \gls{pomc}/\gls{cart} neuron, binding of leptin to its recpetor causes a depolarisation of the neuron \citep{Cowley2001}.
Together with the indirect effect from the \gls{npy}/\gls{agrp} neuron, leptin promotes the \gls{pomc}/\gls{cart} neuron to release $\alpha$-\gls{msh}, and therefore sends a anorexogenic signal to its downstream effector neurons.
\\

@@

The evidence of insulin's involvement in the satiety control was not particularly clear; even though there were strong evidence of obesity with neuron-specific deletion of insulin receptor, and that the insulin level, like leptin, was proportional to the fat mass also suggested the role of insulin in satiety and body weight control (more citation from original paper??) \citep{Barsh2002}.
This was perhaps due to the fact that leptin and insulin used two different signalling pathways in the cell: leptin used the \gls{jak}/\gls{stat} signalling pathway, whereas insulin used the \gls{pi3k} pathway for signalling \citep{Ghilardi1996}.
This was puzzling to the researchers as there seemed to be no converging point of the two hromones in these pathways.

However, leptin, and subsequently insulin, was shown to activate ATP-dep\-endent K$^+$ channel in glucose-responsive neurons in the hypothalamus \citep{Spanswick1997, Spanswick2000}.
The activation of K$^+$ channel provided evidence for the two pathways to act similarly on the cell, at least for an acute response, suggesting a convergence in the pathway response by the two hormones, and therefore their role in satiety control.
\\

\noindent
The last hormone is the \gls{pyy}, a peptide hormone released by the distal gastrointestinal tract that produces an anorexogenic signal.

\gls{pyy} is a gut hormone that is secreted postprandially, and it is released at levels proportional to the calorie content of the meal (original citation, Adrian1985 gastroenterology).
\gls{y2r} is an inhibitory presynaptic receptor that is highly expressed in the \gls{npy}/\gls{agrp} neuron, and is the target of the \gls{pyy} hormone \citep{Batterham2002}.
\citet{Batterham2002} showed that \gls{pyy} decreased the expression of \gls{npy} in the \gls{npy}/\gls{agrp} neuron, and activated the \gls{pomc}/\gls{cart} neuron by membrane depolarisation.
The two mechanisms of \gls{pyy} produces an anorexogenic signal and encourages the individual to stop eating.
